Untitled

### 2025-03-14 script/r/draft.Rmd
maj
rename data file

saveRDS(data_final_r, file="data/data_rds/data_27_02_25.rds")

write_dta(data_final_r, "data/data_dta/data_27_02_25.dta")
```

>>>>

data_final <- readRDS("data/data_rds/data_27_02_25.rds")

data_final%<>%
  ungroup()

data_final%<>%
  mutate(desert_region_tv=desert_region*tv,
         mountain_region_tv=mountain_region*tv)

saveRDS(data_final, file="data/data_rds/data_final.rds")

write_dta(data_final, "data/data_dta/data_final.dta")
```
